\ldots

### 2016-02-09 paper.tex
Typos

For tasks that involve composition, we test the following operators: \textbf{addition}
and \textbf{multiplication} \cite{mitchell2010composition}; \textbf{Kronecker} \cite{Grefenstette:2011:ETV:2140490.2140497}; \textbf{Relational} \cite{Grefenstette:2011:ESC:2145432.2145580}; \textbf{Copy object} and \textbf{Copy subject} \cite{Kartsaklis12aunified}; \textbf{Frobenious addition}, \textbf{Frobenious multiplication} and \textbf{Frobenious outer} \cite{kartsadrqpl2014}.

@@

In general, model performance depends on vector dimensionality. It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth high dimensional spaces ($k > 1$, $\alpha = 0.75$). However, these heuristics do not guarantee the best possible result for \SPMI/ and \NSPMI/ because of high variance of the corresponding scores. Based on this we suggest to use \logNSPMI/ with the dimensionality of at least 20K to ensure good performance on lexical tasks.

@@

>>>>

For tasks that involve composition, we test the following operators: \textbf{addition}
and \textbf{multiplication} \cite{mitchell2010composition}; \textbf{Kronecker} \cite{Grefenstette:2011:ETV:2140490.2140497}; \textbf{Relational} \cite{Grefenstette:2011:ESC:2145432.2145580}; \textbf{Copy object} and \textbf{Copy subject} \cite{Kartsaklis12aunified}; \textbf{Frobenius addition}, \textbf{Frobenius multiplication} and \textbf{Frobenius outer} \cite{kartsadrqpl2014}.

@@

In general, model performance depends on vector dimensionality (the best setup with 50K dimensions is better than the best setup with 1K dimensions by 0.03 on SimLex-999). It is beneficial to experiment with dense and unsmoothed low dimensional spaces ($k < 1$, global context probability); and sparse and smooth high dimensional spaces ($k > 1$, $\alpha = 0.75$). However, these heuristics do not guarantee the best possible result for \SPMI/ and \NSPMI/ because of high variance of the corresponding scores. Based on this we suggest to use \logNSPMI/ with the dimensionality of at least 20K to ensure good performance on lexical tasks.

@@

\section{Compositional experiments}
\label{sec:compositional-experiments}

\input{figures/emnlp13-ppmi-performance}
